---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# saeHB.unit

<!-- badges: start -->

[![CRAN status](https://www.r-pkg.org/badges/version/saeHB.unit)](https://CRAN.R-project.org/package=saeHB.unit) [![check-standard](https://github.com/Alfrzlp/saeHB.unit/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/Alfrzlp/saeHB.unit/actions/workflows/check-standard.yaml)

<!-- badges: end -->

# Author

Azka Ubaidillah, Ridson Al Farizal P

# Maintainer

Ridson Al Farizal P \<alfrzlp\@gmail.com\>

# Description

We designed this package to provide function for unit level of small area estimation (Battese, Harter and Fuller model) using hierarchical Bayesian (HB) method. It also provides datasets generated by data generation (`dummy_unit` and `dummy_area`) and real dataset (`cornsoybean` and `cornsoybeanmean`). The `rjags` package is employed to obtain parameter estimates

# Installation

You can install the development version of saeHB.unit from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("Alfrzlp/saeHB.unit")
```

Or you can install cran version with

```{r, eval=FALSE}
install.packages(saeHB.unit)
```

## Example 1

This is a basic example which shows you how to solve a common problem:

```{r warning=FALSE, message=FALSE}
library(saeHB.unit)
library(ggplot2)
library(dplyr)
library(tidyr)
library(sae)

windowsFonts(
  poppins = windowsFont('poppins')
)
```

### Data
```{r}
glimpse(cornsoybean)
glimpse(cornsoybeanmeans)
```

```{r}
Xarea <- cornsoybeanmeans %>%
   dplyr::select(
      County = CountyIndex,
      CornPix = MeanCornPixPerSeg,
      SoyBeansPix = MeanSoyBeansPixPerSeg
   )
head(Xarea)
```
### EBLUP model
```{r, cahce = TRUE}
Popn <- cornsoybeanmeans %>% 
  dplyr::select(CountyIndex, PopnSegments)

corn_eblup <- pbmseBHF(
  CornHec ~ CornPix + SoyBeansPix,
  dom = County,
  meanxpop = Xarea, popnsize = Popn, data = cornsoybean, B = 50
)

rse_eblup <- sqrt(corn_eblup$mse$mse) * 100 / corn_eblup$est$eblup$eblup

```

### HB model
```{r echo=TRUE,cache=TRUE, message=FALSE, fig.height=3}
corn_hb <- hb_unit(
   CornHec ~ SoyBeansPix + CornPix,
   data_unit = cornsoybean,
   data_area = Xarea,
   domain = "County",
   iter.update = 20
)
```

### Comparison of estimates and RSE
```{r, dpi=500, fig.height=3, fig.width=7}
data.frame(
  id = 1:12,
  hb = corn_hb$Est$MEAN,
  eblup = corn_eblup$est$eblup$eblup
) %>%
  pivot_longer(-1, names_to = "metode", values_to = "rse") %>%
  ggplot(aes(x = id, y = rse, col = metode)) +
  geom_line() +
  scale_color_discrete(
    labels = c('EBLUP', 'HB')
  ) +
  labs(col = NULL, y = 'Estimate', x = 'County', title = 'Comparison of estimates') +
  theme(
    text = element_text(family = 'poppins'),
    axis.ticks.x = element_blank(),
    plot.title = element_text(face = 2, vjust = 0),
    plot.subtitle = element_text(colour = 'gray30', vjust = 0)
  )
```

```{r, dpi=500, fig.height=3, fig.width=7}
data.frame(
  id = 1:12,
  hb = corn_hb$Est$SD * 100 / corn_hb$Est$MEAN,
  eblup = rse_eblup
) %>%
  pivot_longer(-1, names_to = "metode", values_to = "rse") %>%
  ggplot(aes(x = id, y = rse, col = metode)) +
  geom_line() +
  scale_color_discrete(
    labels = c('EBLUP', 'HB')
  ) +
  labs(col = NULL, y = 'RSE', x = 'County', title = 'Comparison of RSE') +
  theme(
    text = element_text(family = 'poppins'),
    axis.ticks.x = element_blank(),
    plot.title = element_text(face = 2, vjust = 0),
    plot.subtitle = element_text(colour = 'gray30', vjust = 0)
  )
```

## Example 2

### Data

```{r}
head(dummy_unit)
```

```{r}
head(dummy_area)
```
### Model
```{r, cache=TRUE}
hb_model <- hb_unit(
  formula = y_di ~ x1 + x2,
  data_unit = dummy_unit,
  data_area = dummy_area,
  domain = "domain",
  iter.update = 30,
  plot = FALSE
)
```

This dataset contains NA in 5 domains out of 30 domains.
```{r}
dummy_unit %>% 
  dplyr::filter(is.na(y_di)) %>% 
  sample_n(size = 5)
```
```{r}
dummy_unit %>% 
  dplyr::filter(is.na(y_di)) %>% 
  distinct(domain)
```


## Autocorelation, Trace and Density plot
```{r, fig.height=3}
saeHB.unit::autoplot(hb_model)
```

## Coefficients
```{r}
summary(hb_model)
```

```{r, dpi=500, fig.height=3, fig.width=7}
data.frame(
  id = 1:30,
  hb = hb_model$Est$MEAN,
  parameter = dummy_area$parameter
) %>%
  pivot_longer(-1, names_to = "metode", values_to = "rse") %>%
  ggplot(aes(x = id, y = rse, col = metode)) +
  geom_line() +
  geom_vline(xintercept = c(14, 16, 22, 27, 29), color = 'red', alpha = 0.2, lwd = 3) +
  scale_color_discrete(
    labels = c('HB with NA', 'Parameter')
  ) +
  labs(col = NULL, y = 'Estimate', x = 'County', title = 'Comparison of estimates') +
  theme(
    text = element_text(family = 'poppins'),
    axis.ticks.x = element_blank(),
    plot.title = element_text(face = 2, vjust = 0),
    plot.subtitle = element_text(colour = 'gray30', vjust = 0)
  )
```

# References

-   Battese, G. E., Harter, R. M., & Fuller, W. A. (1988). An error-components model for prediction of county crop areas using survey and satellite data. Journal of the American Statistical Association, 83(401), 28-36.

-   Rao, J. N., & Molina, I. (2015). Small area estimation. John Wiley & Sons.
